Meta RL analyses

### 2019-01-07 meta_RL_analyses.Rmd
Similarly null results for only one heldout

result_subdirs = c("nometa", "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one", 
                   "basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one")

@@

@@

  if (!is.null(baseline_data)) {
    p = p + 
      annotate("segment",
               x=(1:5)-0.5, xend=(1:5)+0.5,
               y=simple_baselines$expected_reward,
               yend=simple_baselines$expected_reward,
               linetype=3, alpha=0.5) 
  }

@@

reward_d = reward_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) )
```

@@

sweep_d = sweep_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) )
```

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

@@

```{r}
meta_d = load_d(results_dir, c("basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one"), num_runs, "new_meta_true_losses")

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout)))
```

>>>>

result_subdirs = c("nometa", "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho")

@@

new_game_strs_only_one_ho = c('game_straight_flush_l_1_bv_0_sr_0')

@@

  if (!is.null(baseline_data)) {
    p = p + 
      annotate("segment",
               x=(1:5)-0.5, xend=(1:5)+0.5,
               y=simple_baselines$expected_reward,
               yend=simple_baselines$expected_reward,
               linetype=1, alpha=0.5) 
  }

@@

reward_d = reward_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho))
```

@@

sweep_d = sweep_d %>%

  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = (is_default & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) | (is_only_one & game_str %in% new_game_strs_only_one) | (is_only_one_ho & game_str %in% new_game_strs_only_one_ho))
```

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic_only_one_ho", "nometa_only_one_ho")), aes(x=size, color=run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

@@

```{r}
meta_d = load_d(results_dir, c("basic", "basic_su_heldout", "basic_random_holdout_longer", "basic_only_one", "basic_only_one_ho"), num_runs, "new_meta_true_losses")

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout))| (is_only_one_ho & (source %in% new_game_strs_only_one_ho | target %in% new_game_strs_only_one_ho)))
```
